---
title: | 
  | **A *dated* review with R** 
  | Apps, databases, calibrations and analysis
  | for radiocarbon and dendrochronological data
author: "Thomas Huet"
runtime: shiny
output: 
  html_document:
    # css: style.css
    highlight: tango
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 19, fig.height = 14)
library(kableExtra) 
library(dplyr)
library(knitr)
# library(magick)
# library(c14bazAAR)
# library(grDevices)
# library(sp)
# library(leaflet)
# library(Bchron)
mandat.fields <- c("labnr", "c14age", "c14std", "lon", "lat")
# GHimgs <- "https://github.com/zoometh/C14/tree/main/docs/imgs/"
# panel.map <- image_read("docs/imgs/panel_map.png")
# panel.map.coords <- image_read("docs/imgs/panel_map_coords.png")
# panel.calib <- image_read("docs/imgs/panel_calib.png")
```

# Dendrochronological data

As radiocarbon data, dendrochronological open database can be retrieve from the web and mapped. For example, the database of the British [Archaeology Data Service](https://archaeologydataservice.ac.uk/archives/view/vag_dendro/index.cfm) can be download. Then, the database need to be cleaned. After what, the original British National Grid coordinates are converted to lat/long coordinates with the packages [rnrfa](https://cran.r-project.org/web/packages/rnrfa/index.html) and [sf](https://cran.r-project.org/web/packages/sf/index.html)

Shiny and Leaflet allow, for example, to select data filtered on a year threshold, for example
the year of the battle of Agincourt: 1415

```{r echo = TRUE, warning=FALSE}
n_occur <- data.frame(table(df.tot$LabCode))
n_occur <- n_occur[n_occur$Freq > 1,]
n_occur
```

See were is my text...HERE !